Why, when and how to latent mean center variables in multilevel models

### 2022-11-23 ms.Rmd
Acknowledgements

---
title: TITLE
shorttitle: SHORT TITLE
leftheader: SHORT TITLE
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - role mcrole
  - name: Author McAuthor
    affiliation: 2
    address: Address McAddress
    email: email@mcemail.com
    role:
      - role mcrole

@@

>>>>

---
title: Why, when and how to latent mean center variables in multilevel models
shorttitle: Latent mean centering
leftheader: Latent mean centering
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - role mcrole
  - name: Author McAuthor
    affiliation: 2
    address: Address McAddress
    email: email@mcemail.com
    role:
      - role mcrole

@@

# Acknowledgements

We would like to thank Mauricio Garnier-Villarre, Simon Brauer, Ethan McCormick, and everyone else who contributed to the discussion and development of the correct brms syntax on the Stan discussion board (https://discourse.mc-stan.org/t/latent-mean-centering-latent-covariate-models-in-brms/29424). Special thanks to Mauricio Garnier-Villarre for being the first to post the syntax that the code here was based on. We believe developing methods and theories collaboratively, and in the open, to be a fruitful path forward in better understanding human behavior and how to best model it.
